A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-07-29 tidyindex.qmd
various changes

To construct an index, experts typically first define an underlying concept of interest to measure. This concept is latent and often without direct measure but of social and public importance. Relevant and available variables are then defined and collected for measuring the concept and combined as an index using statistical methods. Many decisions are factored into the construction process of an index. For example, decision on which variables to include may depend on the data availability and the choice in other similar indexes. In indexes constructed from linear combination of variables, decisions need to be made on the weight assigned to each variable. In the case of a drought index, analysts may need to decide among similar indexes, on the time scale to aggregate precipitation, and the distribution used to fit the data. All these decisions can introduce uncertainty to the index and lead to different interpretation and actions in operation.

To understand how different factors contribute to the uncertainty of an index, it needs to be broken down into its fundamental building blocks to analyse the effect of each component. Indexes from various disciplines, i.e. [...] seems very different, can be boiled down into a [...]. Such decomposition of indexes standardise the index construction pipeline and offers benefit for comparing among indexes. In social indexes, the OECD handbook [@oecd_handbook_2008] has provided a set of steps for constructing composite socio-economic indexes, but there is a need to extend these guidelines to accommodate more complex construction steps required for indexes in general.

@@

An overview of the pipeline is given in @fig-pipeline-steps to illustrate the construction from raw data to the final indexes.
The pipeline includes eight modules for operations in the spatial, temporal, and multivariate aspects of the data as well as modules for comparing and communicating indexes.
Analysts are free to select the modules they need and arrange them in the order they see fit to construct indexes.
While the starting point of the pipeline is raw data, there are steps prior to this that are crucial to the success of an index. 
For example, the defined index needs to be useful for measuring the concept of interest and variables need to be collected from reliable sources with proper quality control.

  * align the spatial resolution and temporal frequency of data collected from different satellite products
  * obtain and clean variables from countries, potentially aggregate from regional data into country level
  * merge ground-based and satellite-based data

Before elaborating each of the eight pipeline modules as subsections, the data notation will be first introduced. Let $\mathbf{x}(\mathbf{s};\mathbf{t})$ denote the raw data with spatial, temporal, and multivariate aspects: the spatial dimension $\mathbf{s} =  (s_1, s_2, \cdots, s_n)^\prime$ is defined in the 2D space: $\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2$, the temporal dimension $\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime$ is defined in the 1D space: $\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}$. When more than one variable is involved, the multivariate data can also be written as: $\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime$.

@@

where $p^* = 1, 2, \cdots, P^*$ and $p = 1, 2, \cdots, P$ reduce the variable dimension from $P$ to $P^*$. 
The most commonly used dimension reduction technique is Principal Component Analysis (PCA), also called Empirical Orthogonal Function (EOF) in earth science. It can be seen as a special case of weighting, where variables are summed up in a linear combination: $$x_{p^*}(\mathbf{s}; \mathbf{t}) = \sum_{p = 1}^{P}\lambda_{p}x_p(\mathbf{s};\mathbf{t}),$$ with restrictions imposed on the weight coefficient: $\sum_{p=1}^P\lambda_p^2 = 1$. In other cases of weighting, the coefficients can be as simple as giving equal weight to each variables.

@@

```{r eval = FALSE}
dt <- tidyindex::gggi %>% 
  dplyr::select(country: political_empowerment) %>%
  filter(region %in% c("Sub-Saharan Africa")) %>%
  arrange(index) 
colnames(dt) <- c(colnames(dt)[1:4], "economy", "education", "health", "politics")

w_proj2idx <- function(w){w/sum(w)}
w_idx2proj <- function(w){w/(sqrt(sum(w^2))) %>% matrix(nrow = length(w))}
find_next <- function(matrix){
  start <- matrix(c(0.25, 0.25, 0.25, 0.25), ncol = 1)
  tourr:::step_angle(tourr:::geodesic_info(start, matrix), 0.4)
}
b <- array(dim = c(4, 1, 9))
b[,,c(1,3,5,7,9)] <- matrix(c(0.25, 0.25, 0.25, 0.25), ncol = 1) %>% w_idx2proj()
b[,,2] <- matrix(c(0.5, 0.2, 0.2, 0.1), ncol = 1) %>% find_next()
b[,,4] <- matrix(c(0.2, 0.5, 0.2, 0.1), ncol= 1) %>% find_next()
b[,,6] <- matrix(c(0.1, 0.2, 0.5, 0.2), ncol= 1) %>% find_next()
b[,,8] <- matrix(c(0.15, 0.2, 0.15, 0.5), ncol = 1) %>% find_next()

render(
  dt[,5:8], planned2_tour(b), dev = "png",
  display_idx(cex = 2, label_cex = 2,
              label = dt$country, abb_vars = FALSE),
  width = 800, height = 1300, apf = 1/20, frames = 100,
  here::here("figures/idx-tour/idx-tour-%03d.png")
)

gifski::gifski(
  list.files(here::here("figures/idx-tour"), full.names = TRUE),
  gif_file = here::here("figures/idx-tour.gif"),
  delay = 0.15, width = 800, height = 1300)

@@

```{r fig-idx-tour, fig.align='center', fig.height= 12, fig.width=12}
#| fig-cap: "Five frames selected from varying the linear weights of four dimensions in Global Gender Gap Index. The weights vary slightly from the official simple average weights (0.25, 0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full animation is available at https://vimeo.com/847874016?share=copy."
frames <- c("001", "013", "037", "061", "085")
ani <- paste0(here::here("figures/"), "idx-tour/", "idx-tour-", frames, ".png")
rl <- lapply(ani, png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
wrap_plots(gl, ncol = 3) 
```

>>>>

To construct an index, experts typically first define an underlying concept of interest to measure. This concept is latent and often without direct measure but of social and public importance. Relevant and available variables are then defined, collected, and combined as an index using statistical methods to approximate the concept. This construction process is often not straight forward and many decisions need to be made, whether explicitly or not. For example, decision on which variables to include may depend on the data availability and the choice in other similar indexes. Indexes constructed from linear combination of variables need to decide on the weight assigned to each variable. Some indexes have a spatial and/or temporal component and variables can be aggregated to different spatial resolutions and temporal scales for different monitoring purpose. These decisions can result in different index values and have different practical implication.

To be able to test different decision choices systematically for an index, the index needs to be broken down into its fundamental building blocks to analyse the effect of each component. Such decomposition of indexes standardise the index construction pipeline and offers benefit for comparing among indexes and calculate index uncertainty. In social indexes, the OECD handbook [@oecd_handbook_2008] has provided a set of steps for constructing composite socio-economic indexes, but there is a need to extend these guidelines to accommodate more complex construction steps required for indexes in general.

@@

An overview of the pipeline is given in @fig-pipeline-steps to illustrate the construction from raw data to the final indexes.
The pipeline includes eight modules for operations in the spatial, temporal, and multivariate aspects of the data as well as modules for comparing and communicating indexes.
Analysts can choose a subset of modules and reorder them as needed to construct an index.

Data pre-processing may happen before the start of the index pipeline to prepare multivariate data from different locations/ countries ready for constructing an index. For remote sensing data, it includes aligning the spatial resolution and temporal frequency of data collected from different satellite products, or merging in-situ stations with the satellite data.

The notation used for introducing the pipeline modules is as follows. Let $\mathbf{x}(\mathbf{s};\mathbf{t})$ denote the raw data with spatial, temporal, and multivariate aspects: the spatial dimension $\mathbf{s} =  (s_1, s_2, \cdots, s_n)^\prime$ is defined in the 2D space: $\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2$, the temporal dimension $\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime$ is defined in the 1D space: $\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}$. When more than one variable is involved, the multivariate data can also be written as: $\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime$.

@@

where $p^* = 1, 2, \cdots, P^*$ and $p = 1, 2, \cdots, P$ reduce the variable dimension from $P$ to $P^*$. 
The most commonly used dimension reduction technique is Principal Component Analysis (PCA). It can be seen as a special case of weighting, where variables are summed up in a linear combination: $$x_{p^*}(\mathbf{s}; \mathbf{t}) = \sum_{p = 1}^{P}\lambda_{p}x_p(\mathbf{s};\mathbf{t}),$$ with restrictions imposed on the weight coefficient: $\sum_{p=1}^P\lambda_p^2 = 1$. In other cases of weighting, the coefficients can be as simple as giving equal weight to each variables.

@@

```{r eval = FALSE}
dt <- tidyindex::gggi %>% 
  dplyr::select(country: political_empowerment) %>%
  filter(country %in% c("Namibia", "South Africa", "Bangladesh", "Botswana",
                        "Ethiopia", "Kenya", "Senegal", "Afghanistan")) %>%
  arrange(index) 
colnames(dt) <- c(colnames(dt)[1:4], "economy", "education", "health", "politics")

w_proj2idx <- function(w){w/sum(w)}
w_idx2proj <- function(w){w/(sqrt(sum(w^2))) %>% matrix(nrow = length(w))}
find_next <- function(matrix){
  start <- matrix(c(0.25, 0.25, 0.25, 0.25), ncol = 1)
  tourr:::step_angle(tourr:::geodesic_info(start, matrix), 0.4)
}
b <- array(dim = c(4, 1, 9))
b[,,c(1,3,5,7,9)] <- matrix(c(0.25, 0.25, 0.25, 0.25), ncol = 1) %>% w_idx2proj()
b[,,2] <- matrix(c(0.7, 0.1, 0.1, 0.1), ncol = 1) %>% find_next()
b[,,4] <- matrix(c(0.1, 0.7, 0.1, 0.1), ncol= 1) %>% find_next()
b[,,6] <- matrix(c(0.1, 0.1, 0.5, 0.1), ncol= 1) %>% find_next()
b[,,8] <- matrix(c(0.1, 0.1, 0.1, 0.5), ncol = 1) %>% find_next()

render(
  dt[,5:8], planned2_tour(b), dev = "png",
  display_idx(cex = 4, label_cex = 3.5, panel_height_ratio = c(3,1), 
              axis_cex = 2.5, weight_cex = 3, label_col = "grey70", 
              label = dt$country, abb_vars = FALSE),
  width = 900, height = 900, apf = 1/20, frames = 100,
  here::here("figures/idx-tour/idx-tour-%03d.png")
)

gifski::gifski(
  list.files(here::here("figures/idx-tour"), full.names = TRUE),
  gif_file = here::here("figures/idx-tour.gif"),
  delay = 0.15, width = 900, height = 900)

@@

```{r fig-idx-tour, fig.align='center', fig.height=8} 
#| fig-cap: "Five frames selected from varying the linear weights of four dimensions in Global Gender Gap Index. The weights vary slightly from the official simple average weights (0.25, 0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full animation is available at https://vimeo.com/847874016?share=copy."
frames <- c("001", "013", "037", "061", "085")
ani <- paste0(here::here("figures/"), "idx-tour/", "idx-tour-", frames, ".png")
rl <- lapply(ani, png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
wrap_plots(gl, ncol = 2)  
```

### 2023-07-29 tidyindex.tex
various changes

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
\begin{itemize}
\tightlist
\item
  indexes, useful, quantify severity, early monitoring,
\item
  A huge number of indexes have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indexes are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indexes
  from spatio-temporal data,
\item
  This allows all the indexes to be constructed through a uniform data
  pipeline and different indexes to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indexes into small building blocks shared by most of the indexes.
\item
  The framework will be demonstrated with drought indexes as examples,
  but appliable in general to environmental indexes constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

To construct an index, experts typically first define an underlying
concept of interest to measure. This concept is latent and often without
direct measure but of social and public importance. Relevant and
available variables are then defined and collected for measuring the
concept and combined as an index using statistical methods. Many
decisions are factored into the construction process of an index. For
example, decision on which variables to include may depend on the data
availability and the choice in other similar indexes. In indexes
constructed from linear combination of variables, decisions need to be
made on the weight assigned to each variable. In the case of a drought
index, analysts may need to decide among similar indexes, on the time
scale to aggregate precipitation, and the distribution used to fit the
data. All these decisions can introduce uncertainty to the index and
lead to different interpretation and actions in operation.

To understand how different factors contribute to the uncertainty of an
index, it needs to be broken down into its fundamental building blocks
to analyse the effect of each component. Indexes from various
disciplines, i.e.~{[}\ldots{]} seems very different, can be boiled down
into a {[}\ldots{]}. Such decomposition of indexes standardise the index
construction pipeline and offers benefit for comparing among indexes. In
social indexes, the OECD handbook (OECD, European Union, and Joint
Research Centre - European Commission 2008) has provided a set of steps
for constructing composite socio-economic indexes, but there is a need
to extend these guidelines to accommodate more complex construction
steps required for indexes in general.

@@

An overview of the pipeline is given in Figure~\ref{fig-pipeline-steps}
to illustrate the construction from raw data to the final indexes. The
pipeline includes eight modules for operations in the spatial, temporal,
and multivariate aspects of the data as well as modules for comparing
and communicating indexes. Analysts are free to select the modules they
need and arrange them in the order they see fit to construct indexes.
While the starting point of the pipeline is raw data, there are steps
prior to this that are crucial to the success of an index. For example,
the defined index needs to be useful for measuring the concept of
interest and variables need to be collected from reliable sources with
proper quality control.

\begin{itemize}
\tightlist
\item
  align the spatial resolution and temporal frequency of data collected
  from different satellite products
\item
  obtain and clean variables from countries, potentially aggregate from
  regional data into country level
\item
  merge ground-based and satellite-based data
\end{itemize}

Before elaborating each of the eight pipeline modules as subsections,
the data notation will be first introduced. Let
\(\mathbf{x}(\mathbf{s};\mathbf{t})\) denote the raw data with spatial,
temporal, and multivariate aspects: the spatial dimension
\(\mathbf{s} = (s_1, s_2, \cdots, s_n)^\prime\) is defined in the 2D
space: \(\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2\), the
temporal dimension \(\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime\) is
defined in the 1D space:
\(\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}\). When more than
one variable is involved, the multivariate data can also be written as:
\(\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime\).

@@

where \(p^* = 1, 2, \cdots, P^*\) and \(p = 1, 2, \cdots, P\) reduce the
variable dimension from \(P\) to \(P^*\). The most commonly used
dimension reduction technique is Principal Component Analysis (PCA),
also called Empirical Orthogonal Function (EOF) in earth science. It can
be seen as a special case of weighting, where variables are summed up in
a linear combination:
\[x_{p^*}(\mathbf{s}; \mathbf{t}) = \sum_{p = 1}^{P}\lambda_{p}x_p(\mathbf{s};\mathbf{t}),\]
with restrictions imposed on the weight coefficient:
\(\sum_{p=1}^P\lambda_p^2 = 1\). In other cases of weighting, the
coefficients can be as simple as giving equal weight to each variables.

@@

The Global Gender Gap Index (GGGI), published annually by the World
Economic Forum, measures gender parity by assessing relative gaps
between men and women in four key areas: Economic Participation and
Opportunity, Educational Attainment, Health and Survival, and Political
Empowerment (World Economic Forum 2023). The index is composed of 14
variables, expressed as female-to-male ratios, which are first
aggregated in a linear combination into the four dimensions using the
weight from the \texttt{V-weight} column in
Table~\ref{tbl-gggi-weights}. The weight is calculated as the inverse of
the standard deviation of each variable and scaling to sum to 1 within
each dimension to allow a one percentage point change in the standard
deviation of each variable to contribute equally to the index. The four
dimensions are then aggregated in another linear combination with equal
weight tp obtain the index. The 2023 GGGI data is available from the
Global Gender Gap Report 2023 in the country's economy profile and can
be accessed in R via the \texttt{tidyindex} package as \texttt{gggi},
along with the corresponding weights \texttt{gggi\_weights}.

>>>>

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
\begin{itemize}
\tightlist
\item
  indexes, useful, quantify severity, early monitoring,
\item
  A huge number of indexes have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indexes are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indexes
  from spatio-temporal data,
\item
  This allows all the indexes to be constructed through a uniform data
  pipeline and different indexes to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indexes into small building blocks shared by most of the indexes.
\item
  The framework will be demonstrated with drought indexes as examples,
  but appliable in general to environmental indexes constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, enhanced, boxrule=0pt, interior hidden, breakable]}{\end{tcolorbox}}\fi

@@

To construct an index, experts typically first define an underlying
concept of interest to measure. This concept is latent and often without
direct measure but of social and public importance. Relevant and
available variables are then defined, collected, and combined as an
index using statistical methods to approximate the concept. This
construction process is often not straight forward and many decisions
need to be made, whether explicitly or not. For example, decision on
which variables to include may depend on the data availability and the
choice in other similar indexes. Indexes constructed from linear
combination of variables need to decide on the weight assigned to each
variable. Some indexes have a spatial and/or temporal component and
variables can be aggregated to different spatial resolutions and
temporal scales for different monitoring purpose. These decisions can
result in different index values and have different practical
implication.

To be able to test different decision choices systematically for an
index, the index needs to be broken down into its fundamental building
blocks to analyse the effect of each component. Such decomposition of
indexes standardise the index construction pipeline and offers benefit
for comparing among indexes and calculate index uncertainty. In social
indexes, the OECD handbook (OECD, European Union, and Joint Research
Centre - European Commission 2008) has provided a set of steps for
constructing composite socio-economic indexes, but there is a need to
extend these guidelines to accommodate more complex construction steps
required for indexes in general.

@@

An overview of the pipeline is given in Figure~\ref{fig-pipeline-steps}
to illustrate the construction from raw data to the final indexes. The
pipeline includes eight modules for operations in the spatial, temporal,
and multivariate aspects of the data as well as modules for comparing
and communicating indexes. Analysts can choose a subset of modules and
reorder them as needed to construct an index.

Data pre-processing may happen before the start of the index pipeline to
prepare multivariate data from different locations/ countries ready for
constructing an index. For remote sensing data, it includes aligning the
spatial resolution and temporal frequency of data collected from
different satellite products, or merging in-situ stations with the
satellite data.

The notation used for introducing the pipeline modules is as follows.
Let \(\mathbf{x}(\mathbf{s};\mathbf{t})\) denote the raw data with
spatial, temporal, and multivariate aspects: the spatial dimension
\(\mathbf{s} = (s_1, s_2, \cdots, s_n)^\prime\) is defined in the 2D
space: \(\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2\), the
temporal dimension \(\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime\) is
defined in the 1D space:
\(\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}\). When more than
one variable is involved, the multivariate data can also be written as:
\(\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime\).

@@

where \(p^* = 1, 2, \cdots, P^*\) and \(p = 1, 2, \cdots, P\) reduce the
variable dimension from \(P\) to \(P^*\). The most commonly used
dimension reduction technique is Principal Component Analysis (PCA). It
can be seen as a special case of weighting, where variables are summed
up in a linear combination:
\[x_{p^*}(\mathbf{s}; \mathbf{t}) = \sum_{p = 1}^{P}\lambda_{p}x_p(\mathbf{s};\mathbf{t}),\]
with restrictions imposed on the weight coefficient:
\(\sum_{p=1}^P\lambda_p^2 = 1\). In other cases of weighting, the
coefficients can be as simple as giving equal weight to each variables.

@@

The Global Gender Gap Index (GGGI), published annually by the World
Economic Forum, measures gender parity by assessing relative gaps
between men and women in four key areas: Economic Participation and
Opportunity, Educational Attainment, Health and Survival, and Political
Empowerment (World Economic Forum 2023). The index is composed of 14
variables, expressed as female-to-male ratios, which are first
aggregated in a linear combination into the four dimensions using the
weight from the \texttt{V-weight} column in
Table~\ref{tbl-gggi-weights}. The weight is calculated as the inverse of
the standard deviation of each variable and scaling to sum to 1 within
each dimension to allow a one percentage point change in the standard
deviation of each variable to contribute equally to the index. The four
dimensions are then aggregated in another linear combination with equal
weight to obtain the index. The 2023 GGGI data is available from the
Global Gender Gap Report 2023 in the country's economy profile and can
be accessed in R via the \texttt{tidyindex} package as \texttt{gggi},
along with the corresponding weights \texttt{gggi\_weights}.
